Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/tex/advanced.tex
* added some introduction text to the tracers part of the manual
Signed-off-by: Lttlemoi <lttlemoi+git@gmail.com>

\section{Tracing}
The tracers generate output during the simulation.
\label{sec:Tracing}
\paragraph{The Tracing interface}
The interface consists of only a handful methods.
\paragraph{Custom set of tracers}
If the default set of tracers is not satisfactory, then you can select your own set of tracers. The header \path{tracers.h} in the folder \path{src/forwarddeclare} contains the typedef for the default implementation.
\begin{lstlisting}
typedef Tracers<VerboseTracer<CoutWriter>> t_tracerset;
\end{lstlisting}
You can select as many tracers as you want by providing more template arguments. The following example sets the simulator to use two tracers. The first tracer will generate the default verbose output and write it to a file. The second tracer is a custom tracer.
\begin{lstlisting}
typedef Tracers<VerboseTracer<FileWriter>,
                MyTracer> t_tracerset;
\end{lstlisting}
Note that some tracers might need special initialization prior to use, such as the tracers provided by us that make use of the \lstinline{FileWriter} policy.

>>>>

\section{Tracing}
\label{sec:Tracing}
The tracers generate output during the simulation. The default set of tracers will print verbose output to the standard output stream \lstinline{std::cout}.
\paragraph{Custom set of tracers}
If the default set of tracers is not satisfactory, then you can select your own set of tracers. The header \path{tracers.h} in the folder \path{src/forwarddeclare} contains the typedef for the default implementation.
\begin{lstlisting}
typedef Tracers<VerboseTracer<CoutWriter>> t_tracerset;
\end{lstlisting}
You can select as many tracers as you want by providing more template arguments. The following example sets the simulator to use two tracers. The first tracer will generate the default verbose output and write it to a file. The second tracer is a custom tracer.
\begin{lstlisting}
typedef Tracers<VerboseTracer<FileWriter>,
                MyTracer> t_tracerset;
\end{lstlisting}
Note that some tracers might need special initialization prior to use, such as the tracers provided by us that make use of the \lstinline{FileWriter} policy.
